\DeclareDocumentCommand{\newdualentry}{ O{} O{} m m m m } {
        \newglossaryentry{gls-#3}{
                name={#5},
                text={#5\glsadd{#3}},
                description={#6},
                #1
        }
        \newacronym[see={[see:]{gls-#3}},#2]{#3}{#4}{#5\glsadd{gls-#3}}
}


% description
\newglossaryentry{event}
{
        name=process event,
        description={Also called activities. A discrete step in the process.}
}

\newglossaryentry{instance}
{
        name=process instance,
        description={Also called case. A collection of activities that belong to a common entity that is produced by the process.}
}

\newglossaryentry{log}
{
        name=event log,
        description={A collection of event data, that's produced by the process. They are the main input of every process mining venture.}
}
\newglossaryentry{trueprocess}
{
        name=\emph{true} process,
        description={The true data generating process which remains unknown. The term contrasts a modelled process, which seeks to approximate the \emph{true} process' behaviour.}
}


\newglossaryentry{drift}
{
        name=Concept Drift,
        description={The phenomenon of changing processes over time. The changes may occur gradually or sudden and be irregular or recurrent.}
}
\newglossaryentry{rashomon}
{
        name=Rashommon Effect,
        description={Rashomon is a classic Japanese movie in which multiple witnesses tell a different equally valid story about the murder of a samurai. Although, each story acts as a valid explanation, they contradict each other. The same effect may apply to equally valid counterfactuals.}
}
\newglossaryentry{DL}
{
        name=Deep Learning,
        description={A sub-discipline of machine learning which focuses on neural networks as primary tool. The discipline emphasises the research and development of neural network architectures. Data preprocessing and feature engineering play a secondary role.}
}
\newglossaryentry{causalinference}
{
        name=Causal Inference,
        description={A discipline which seeks to incoporate causal relations to model phenomena in the real world.}
}
\newglossaryentry{DM}
{
        name=Data Mining,
        description={XXX}
}
\newglossaryentry{bbm}
{
        name=blackbox model,
        description={A model, whose reasoning pattern is intransparent and incomprehensible for a human observer.}
}
\newdualentry{CSV}{CSV}{Comma Seperated Values}{A structured data format to store information. Every line relates to a data point and every feature is seperated by a seperator. The seperator is commonly a comma but other characters like tabs or semicolons are valid as well.}
\newdualentry{XES}{XES}{eXtensible Event Stream}{An XML-based data format to store event logs. The format was developed and adopted by the IEEE Task Force on Process Mining.}
\newdualentry{NLP}{NLP}{Natural Language Processing}{A discipline that is mainly concerned with the analysis and modelling of natural language.}
\newdualentry{GAN}{GAN}{Generative Adversarial Model}{A model in which two neural network train simultaneously. The generative model tries to generate instance examples, while the discriminative models tries to distinguish real examples from generated ones. Both, the discriminator and the generator can be used in isolation afterwards.}
\newdualentry{PM}{PM}{Process Mining}{A subdiscipline of Data Mining, which uses process logs to analyse and utilise data which was produced by processes.}
\newdualentry{MDP}{MDP}{Markov Decision Process}{A probablistic process which assumes that an agent can influence the outcome of the process by choosing decisions given a state and expecting a return for its performance.}
\newdualentry{MP}{MP}{Markov Process}{A probablistic process whose outcomes depend on the process' state.}
\newdualentry{RL}{RL}{Reinforcement Learning}{An are within Machine Learning, which seeks to allow an intelligent agent to choose the right actions by maximizing the cumulative rewards of a task setting.}
\newdualentry{SCM}{SCM}{Structural Causal Model}{Also called \emph{Structural Equation Model (SEM)}. An SCM is a set of variables and equations. The equations' the relationship of outputs from other equations and the variables. The relationship between functions and variables inform the causal relationship. SCMs can be represented as directed graphs in which nodes describe variables and equations and the vertices dependencies. Furthermore, a SCM can produce a dataset containing all the values thhat where generated.}
\newdualentry{HCI}{HCI}{Human Computer Interaction}{A cross-disciplinary discipline which observes and researches the interfaces and interactions between humans and computers.}


\newdualentry{IS}{IS}{Information System}{XXX}
\newdualentry{BI}{BI}{Business Intelligence}{XXX}
\newdualentry{CPM}{CPM}{Corporate Performance Management}{XXX}
\newdualentry{BPM}{BPM}{Business Process Management}{XXX}
\newdualentry{CPI}{CPI}{Continuous Process Improvement}{XXX}
\newdualentry{TQM}{TQM}{Total Quality Management}{XXX}
\newacronym{XAI}{XAI}{eXplainable AI}
\newacronym{ML}{ML}{Machine Learning}
\newacronym{VAE}{VAE}{Variational Autoencoder}
\newacronym{DMM}{DMM}{Deep Markov Model}
\newacronym{DKF}{DKF}{Deep Kalman Filter}
\newacronym{ELBO}{ELBO}{Evidence Lower-Bound}
\newacronym{HMM}{HMM}{Hidden Markov Model}
\newacronym{PGM}{PGM}{Probalistic Graphical Model}
\newacronym{BPMN}{BPMN}{Business Process Modell Notation}
\newacronym{LSTM}{LSTM}{Long Short-Term Memory}
\newacronym{RNN}{RNN}{Recurrent Neural Network}
\newacronym{CNN}{CNN}{Convolutional Neural Network}
\newacronym{NN}{NN}{Neural Network}

% \begin{document}
% \end{document}